Measuring matter effects in Neutron star - Black hole binaries with Advanced LIGO: a Bayesian study

### 2016-04-13 Paper/paper.tex
added no-mass-gap pop plots + updated old ones

\includegraphics[trim=20 0 0 0, width=1.05\columnwidth]{plots/LambdaMedian_vs_N_AllPopulation}

@@

\includegraphics[width=.9\columnwidth]{plots/LambdaCIWidths_vs_N_AllPopulations_Log_L2000.pdf}
\includegraphics[width=.9\columnwidth]{plots/LambdaCIWidths_vs_N_AllPopulations_Log_L1500.pdf}\\
\includegraphics[width=.67\columnwidth]{plots/LambdaCIWidths_vs_N_AllPopulations_Log_L1000.pdf}
\includegraphics[width=.67\columnwidth]{plots/LambdaCIWidths_vs_N_AllPopulations_Log_L800.pdf}
\includegraphics[width=.67\columnwidth]{plots/LambdaCIWidths_vs_N_AllPopulations_Log_L500.pdf}

@@

>>>>

\includegraphics[trim=20 0 0 0, width=1.02\columnwidth]{plots/LambdaMedian_vs_N_AllPopulation}
\includegraphics[trim=20 0 0 0, width=1.02\columnwidth]{plots/LambdaMedian_vs_N_AstroPopulation}

@@

\includegraphics[width=0.85\columnwidth]{plots/LambdaCIWidths_vs_N_AllPopulations_Log_L2000.pdf}
\includegraphics[width=0.85\columnwidth]{plots/LambdaCIWidths_vs_N_AstroPopulations_Log_L2000.pdf}\\
\includegraphics[width=0.85\columnwidth]{plots/LambdaCIWidths_vs_N_AllPopulations_Log_L1500.pdf}
\includegraphics[width=0.85\columnwidth]{plots/LambdaCIWidths_vs_N_AstroPopulations_Log_L1500.pdf}\\
\includegraphics[width=0.85\columnwidth]{plots/LambdaCIWidths_vs_N_AllPopulations_Log_L1000.pdf}
\includegraphics[width=0.85\columnwidth]{plots/LambdaCIWidths_vs_N_AstroPopulations_Log_L1000.pdf}\\
\includegraphics[width=0.85\columnwidth]{plots/LambdaCIWidths_vs_N_AllPopulations_Log_L800.pdf}
\includegraphics[width=0.85\columnwidth]{plots/LambdaCIWidths_vs_N_AstroPopulations_Log_L800.pdf}\\
\includegraphics[width=0.85\columnwidth]{plots/LambdaCIWidths_vs_N_AllPopulations_Log_L500.pdf}
\includegraphics[width=0.85\columnwidth]{plots/LambdaCIWidths_vs_N_AstroPopulations_Log_L500.pdf}

@@

% \includegraphics[width=.9\columnwidth]{plots/LambdaCIWidths_vs_N_AllPopulations_Log_L2000.pdf}
% \includegraphics[width=.9\columnwidth]{plots/LambdaCIWidths_vs_N_AllPopulations_Log_L1500.pdf}\\
% \includegraphics[width=.67\columnwidth]{plots/LambdaCIWidths_vs_N_AllPopulations_Log_L1000.pdf}
% \includegraphics[width=.67\columnwidth]{plots/LambdaCIWidths_vs_N_AllPopulations_Log_L800.pdf}
% \includegraphics[width=.67\columnwidth]{plots/LambdaCIWidths_vs_N_AllPopulations_Log_L500.pdf}
% \caption{ In the main panel is shown the width of the measured $90\%$ 
